---
title: "Position error"
output:
  bookdown::html_document2:
    number_sections: false

date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## add column  to shp.stat for plotting
shp.stat$plot <- "station"

## get plotting dimensions
dimC <- st_bbox(shp[shp$site == "maisC",])
dimD <- st_bbox(shp[shp$site == "maisD",])

```


```{r}


## plot example for methods
ggplot() + 
  geom_sf(aes(fill = as.character(dens)), color = NA, data = shp.buffer[shp.buffer$station == "c1l1",], lwd = 2) + 
  geom_sf(data = shp.stat[shp.stat$station.id == "c1l1",], pch = 2, color = "white") + 
  scale_fill_viridis_d("station density", direction = -1, option = "rocket", alpha = 0.4) +
  theme_light()

## plot example for methods
ggplot() + 
  geom_sf(aes(fill = as.character(dens)), color = NA, data = shp.buffer[shp.buffer$station %in% c("c1l1", "c2l1"),], lwd = 2) + 
  geom_sf(data = shp.stat[shp.stat$station.id %in% c("c1l1", "c2l1"),], pch = 2, color = "white") + 
  scale_fill_viridis_d("station density", direction = -1, option = "rocket", alpha = 0.4) +
  theme_light()
```

## station denisty raster {.tabset}

### maisC

```{r}
## clip raster to maisC
df.rC <- st_intersection(st_transform(r.shp, crs = crs), st_union(st_buffer(st_transform(shp.stat[shp.stat$station.project_id == "maisC",], crs = crs), dist = rast_buf*1.1)))

## plot raster (= merged polygons)
ggplot() + 
  geom_sf(aes(fill = dens, color = dens), data = df.rC, lwd = 0.1) + 
  geom_sf(data = shp.stat[shp.stat$station.project_id == "maisC",], pch = 2, color = "white") + 
  # geom_sf(data = df[100000:100100,], pch = 1, color = "grey80", alpha = 0.5) + # check whether dimensions are correct
  scale_fill_viridis_c("station density", direction = -1, option = "rocket", na.value = NA) +
  scale_color_viridis_c("station density", direction = -1, option = "rocket", na.value = NA) +
  facet_wrap(~type) +
  annotation_scale(width_hint = 0.2, bar_cols = c("grey60", "white"), color = "grey60") +
  theme_light()
```

### maisD

```{r}
## clip raster to maisD
df.rD <- st_intersection(st_transform(r.shp[r.shp$type == "direct",], crs = crs), st_union(st_buffer(st_transform(shp.stat[shp.stat$station.project_id == "maisD",], crs = crs), dist = rast_buf*1.1)))
## plot raster (= merged polygons)
ggplot() + 
  geom_sf(aes(fill = dens, color = dens), data = df.rD, lwd = 0.1) + 
  geom_sf(data = shp.stat[shp.stat$station.project_id == "maisD",], pch = 2, color = "white") + 
  # geom_sf(data = df[100000:100100,], pch = 1, color = "grey80", alpha = 0.5) + # check whether dimensions are correct
  scale_fill_viridis_c("station density", direction = -1, option = "rocket", na.value = NA) +
  scale_color_viridis_c("station density", direction = -1, option = "rocket", na.value = NA) +
  facet_wrap(~type) +
  annotation_scale(width_hint = 0.2, bar_cols = c("grey60", "white"), color = "grey60") +
  theme_light()
```

# position error per station density (est. positions) {.tabset}

## maisC

```{r}
for(m in unique(df$meth[df$site == "maisC"])) {
  dat <- df[df$site == "maisC" & df$meth == m,]

  print(ggplot(dat) +
    # geom_point(aes(x = dens, y = dist, color = r, group = r),
    #            pch = 1, alpha = 0.2,
    #            position = position_dodge(width = 0.5)) +
    geom_smooth(aes(x = dens, y = PE, group = r, color = r), method = "glm", formula = y ~ poly(x, 2)) +
    ggtitle(paste0(m)) +
    ylab("position error [m]") +
    xlab("station cover") +
    ylim(0, NA) +
    facet_wrap(~Individual, scales = "free_y") +
    scale_color_viridis_d("detection \nrange", end  = 0.9) +
    theme_light())  

}

```

## maisD

```{r}
for(m in unique(df$meth[df$site == "maisD"])) {
  dat <- df[df$site == "maisD" & df$meth == m,]

  print(ggplot(dat) +
    # geom_point(aes(x = dens, y = dist, color = r, group = r),
    #            pch = 1, alpha = 0.2,
    #            position = position_dodge(width = 0.5)) +
    geom_smooth(aes(x = dens, y = PE, group = r, color = r), method = "glm", formula = y ~ poly(x, 2)) +
    ggtitle(paste0(m)) +
    ylab("position error [m]") +
    xlab("station cover") +
    ylim(0, NA) +
    facet_wrap(~Individual, scales = "free_y") +
    scale_color_viridis_d("detection \nrange", end  = 0.9) +
    theme_light())  

}

```


## maisC (raw)

```{r}
for(m in unique(df$meth[df$site == "maisC"])) {
  dat <- df[df$site == "maisC" & df$meth == m,]
  
    print(ggplot(dat) +
      geom_point(aes(x = dens, y = PE, color = r, group = r),
                 pch = 1, alpha = 0.2,
                 position = position_dodge(width = 0.5)) +
      geom_smooth(aes(x = dens, y = PE, group = r, color = r), method = "glm", formula = y ~ poly(x, 2)) +
      ggtitle(paste0(m), subtitle = "mean PE from est. positions (solid)") +
      ylab("position error [m]") +
      xlab("station cover") +
      ylim(0, NA) +
      facet_wrap(~Individual, scales = "free_y") +
      scale_color_viridis_d("detection \nrange", end  = 0.9) +
      theme_light())  
}

```

## maisD (raw)

```{r}
for(m in unique(df$meth[df$site == "maisD"])) {
  dat <- df[df$site == "maisD" & df$meth == m,]
  
    print(ggplot(dat) +
      geom_point(aes(x = dens, y = PE, color = r, group = r),
                 pch = 1, alpha = 0.2,
                 position = position_dodge(width = 0.5)) +
      geom_smooth(aes(x = dens, y = PE, group = r, color = r), method = "glm", formula = y ~ poly(x, 2)) +
      ggtitle(paste0(m), subtitle = "mean PE from est. positions (solid)") +
      ylab("position error [m]") +
      xlab("station cover") +
      ylim(0, NA) +
      facet_wrap(~Individual, scales = "free_y") +
      scale_color_viridis_d("detection \nrange", end  = 0.9) +
      theme_light())  
}

```


# raster
These plots show summarized raster (`r rast_res*rast_inc`x`r rast_res*rast_inc` m resolution) based on positions from testtags with ground truth data (GPS data). Each plot is split by individual (= testtag, e.g. TT090C) and separate plots were made per method (*direct.ab* = directional antenna beams, *omni.ab* = omnidirectional antenna beams, *omni.ml* = omnidirectional mulitlateration, *direct.an* = directional angulation)  

**abbreviations in tabs:**  
- *rp*: raw positions  
- *tp*: true GPS positions  
- *mean*: mean position error  
- *sd*: sd of position error  
- *N*: number of points  


---

## maisC {.tabset}

### mean rp

```{r}
site <- "maisC"
dim <- dimC

## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = mean, color = mean), lwd = 0.1)
    g <- plot.raster(g, leg = "mean \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))
  }
}

```

### median rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = median, color = median), lwd = 0.1)
    g <- plot.raster(g, leg = "median \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}
```

### sd rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = sd, color = sd), lwd = 0.1)
    g <- plot.raster(g, leg = "sd \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```

### N rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = N, color = N), lwd = 0.1)
    g <- plot.raster(g, leg = "N points")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```


### mean tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = mean, color = mean), lwd = 0.1)
    g <- plot.raster(g, leg = "mean \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))
  }
}

```

### median tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = median, color = median), lwd = 0.1)
    g <- plot.raster(g, leg = "median \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}
```

### sd tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = sd, color = sd), lwd = 0.1)
    g <- plot.raster(g, leg = "sd \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```

### N tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = N, color = N), lwd = 0.1)
    g <- plot.raster(g, leg = "N points")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```


## maisD {.tabset}

### mean rp

```{r}
site <- "maisD"
dim <- dimD

## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = mean, color = mean), lwd = 0.1)
    g <- plot.raster(g, leg = "mean \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))
  }
}

```

### median rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = median, color = median), lwd = 0.1)
    g <- plot.raster(g, leg = "median \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}
```

### sd rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = sd, color = sd), lwd = 0.1)
    g <- plot.raster(g, leg = "sd \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```

### N rp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos",], 
              aes(fill = N, color = N), lwd = 0.1)
    g <- plot.raster(g, leg = "N points")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```


### mean tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = mean, color = mean), lwd = 0.1)
    g <- plot.raster(g, leg = "mean \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))
  }
}

```

### median tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = median, color = median), lwd = 0.1)
    g <- plot.raster(g, leg = "median \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}
```

### sd tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = sd, color = sd), lwd = 0.1)
    g <- plot.raster(g, leg = "sd \nposition \nerror")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```

### N tp

```{r}
## plot raster (= merged polygons)
for(m in unique(shp$meth[shp$site == site])) {
  for(d in unique(shp$r[shp$site == site & shp$meth == m])) {
    if(m %in% c("omni.ab", "omni.ml")) type <- "omni"
    if(m %in% c("direct.ab", "direct.an")) type <- "direct"
    
    g <- ggplot() + 
      geom_sf(data = shp[shp$site == site & shp$meth == m & shp$r == d & shp$source == "pos.gps",], 
              aes(fill = N, color = N), lwd = 0.1)
    g <- plot.raster(g, leg = "N points")
    g <- plot.station(g, site = site, type = type, size = 2, stroke = 1)
    print(plot.theme(g))      

  }
}

```