---
title: |
  ARTS - methods
short-title: ARTS_methods
published: "working manuscript"
code-repo: "Access the code, data, and analysis at <https://github.com/m-rieger/MaisLE_ARTS.git>"
correspondence-prefix: "Correspondence concerning this article should be addressed to"
author:
  - name: Mirjam R. Rieger
    email: mrieger@posteo.de
    orcid: 0000-0002-7404-6023
    affiliations: 
      - id: HFR
        name: University of Applied Science
        department:
        city: Rottenburg
        country: Germany
      - id: UT
        name: Eberhard Karls University
        department: Institute of Evolution and Ecology
        city: Tuebingen
        country: Germany
    attributes:
      corresponding: true
      
  - name: Jan Schmitt
    email: xx
    orcid: xx
    affiliations:
      - ref: UT
        
  - name: Paula Machin
    email: xx
    orcid: xx
    affiliations:
      - id: Eurofins
        name: Eurofins MITOX group
        department: Wildlife field services
        city: Dresden
        country: Germany
        
  - name: Johann Musculus
    email: xx
    orcid: xx
    affiliations:
      - ref: Eurofins
        
  - name: Ralf Dittrich
    email: xx
    orcid: xx
    affiliations:
      - ref: Eurofins
        
  - name: Jannis Gottwald
    email: gottwald@trackit.systems
    orcid: xx
    affiliations:
      - id: trackit
        name: tRackIT systems
        department: 
        city: Marburg
        country: Germany

  - name: Jonas Hoechst
    email: hoechst@trackit.systems
    orcid: 0000-0002-7326-2250
    affiliations:
      - ref: trackit               

  - name: Patrick Lampe
    email: lampe@trackit.systems
    orcid: xx
    affiliations:
      - ref: trackit                  
        
abstract: |
  Abstract goes here.
keywords:
  - bird migration
  - radio-telemetry
  - stopover ecology
date: today
bibliography: references.bib
number-sections: false
keep-tex: true
format:
  hikmah-pdf: default # this does not work due to latex problems
  # hikmah-manuscript-pdf: default
  hikmah-manuscript-docx: default
---

<!-- ```{css} -->
<!-- #| echo: false -->
<!-- p { -->
<!--   text-align: justify -->
<!-- } -->
<!-- ``` -->

<!-- rmarkdown::render("R/MaisLE_ARTS.qmd", output_format = "pdf_document") -->
<!-- rmarkdown::render("R/MaisLE_ARTS.qmd", output_format = "word_document") -->

<!-- cite using [@gottwald2019], add BibTeX citation to references.bib   -->

```{r setup, include=F}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE)

## packages
library(tidyverse)
library(kableExtra)
library(sf)
library(leaflet)

## formatting variables
# font size for tables
smallT <- 10
bigT <- 12

tab.site <- read.csv("../data/tabSites.csv", encoding = "latin1")

df.stat <- read.csv("../data/station.csv", encoding = "latin1")
df.stat <- st_as_sf(x = df.stat,                         
           coords = c("station.lon", "station.lat"),
           crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0",
           remove = F)
```



# About {.unnumbered}

Paper to compare different methods for position estimation using directional stations (quadrologgers) and omnidiretional stations (monologgers), mainly based on data from maisC but supplemented with data from maisD and melons (only quadrologgers). 

We aim to publish it in Methods of Ecology and Evolution <https://besjournals.onlinelibrary.wiley.com/journal/2041210x>  


# Abstract {.unnumbered}

# Introduction
Wildlife conservation relies on the information about spatial and temporal distribution of animals (Aarts et al. 2009). The information helps to identify species’ preferred resources and to define their habitat requirements (Falconi et al. 2015). Understanding how animals choose resources based on availability helps to prioritize conservation efforts (de Gabriel Hernando et al., 2021). Conservation decisions on the landscape management increasingly rely on detailed movement data of target species (Cooke et al., 2005). However, the collection of movement data is labor intensive because of the cryptic lifestyles of animals (Kays et al., 2011). Visual observation, which often requires researchers to directly pursue their target animal, can disrupt their natural behavior (Marion et al., 2020). Such a change in behavior can lead to misinterpretation of the actual habitat requirements of the target species. Recent technological advances in low-disturbance methods, however, allow for automated tracking of many species. Because of the high demand for movement data, the development of new tracking systems flourish. Ecologists are facing an unprecedented wealth of movement data. The advanced quality of data marks the beginning of what has been termed the ‘golden era of movement ecology’ (Wilmers et al., 2015; Kays et al., 2015). However, ensuring data quality with emerging tracking systems is challenging because these systems often use different data sources and formats, which usually cannot be integrated directly into existing quality tests. Therefore, the development of methods to analyze the new data structures must keep pace with the development of tracking systems to provide system-specific workflows for validating and processing the large amount of tracking data.  
The two most common technologies to record wildlife movement data are very high-frequency (VHF) telemetry and the Global Positioning System (GPS). Widely used GPS systems use receiver tags that measure the Time of Arrival (ToA) of incoming satellite signals. Satellites make GPS immediately operational over large areas of the world, providing reliable positioning with highly synchronized clocks. However, GPS receiver tags rely on heavy hardware components for data collection and storage. Wildlife tags should not exceed 5% of the animal's body weight to avoid impact on natural behavior (Barron et al., 2010). To save weight, many GPS tags do not transmit data remotely. Users must recapture tagged animals to retrieve logger data. Recapture makes traditional GPS wildlife tracking unsuitable for fast-moving animals such as migratory birds and bats (Kays et al., 2015). Therefore, VHF technology with lighter tags, which only emit signals, often remains the preferred alternative.  
Since the 1960s, radio telemetry using VHF transmitter tags has been the primary method for tracking animal movement (Crewe et al., 2017). The development of lightweight VHF transmitters has extended the scope of tracking systems to many small animals. Scientists are now using miniature transmitters <1 g (Gottwald et al., 2022). The transmitters allow observing the flight paths of animals from a greater distance than is possible with visual observation (Fisher et al., 2020). For animals with low mobility, traditional VHF telemetry using handheld antennas can achieve a positional accuracy of five meters (Crewe et al., 2017), similar to the resolution of standard GPS devices under the open sky (Kerwath et al., 2005). However, handheld telemetry is limited to about 50 position records per day (Kenward, 2000), and each observer can only follow a single animal at a time.  
Automated radio telemetry systems (ARTS) with arrays of autonomous receivers allow us to track multiple animals at once (Paxton et al., 2022). For ARTS studies, a network of passive ground stations with receivers distributes across the study area. The ground stations provide a high flexibility that allows ARTS deployment in different-sized areas. The most comprehensive ARTS, Motus Wildlife Tracking System, operates a network of 325 receiving stations on three continents (Crewe et al., 2017). As a global project, it documents large-scale movements such as bird and bat migration (Motus; https://motus.org). Despite the terrestrial stations, Motus also monitors areas that otherwise only GPS satellites can cover, such as the adjacent open sea. At the regional and landscape level, ARTS operate with fewer receiving stations. Such surveys aim at monitoring small-scale movements of animals, which requires more accurate positioning than the global Motus system. For this reason, ARTS design and structure are tailored to the scientific questions. Kays et al. (2011) installed a 7-station ARTS on the 1567 ha Barro Colorado Island, Panama. The project had to account for site factors that hinder radio signal transmission, like dense forest cover and moist climate. It has been used in various studies, tracking 38 animal species and 2 plant seed species (Kays et al., 2011). Once users overcome the hurdles of individual configuration, such ARTS can provide a large amount of movement data. Yet, ensuring the accuracy of the collected data is a top priority.  
The mean positioning errors of ARTS start at a scale of tens of meters (Ward et al., 2013). A fine-scale setup by Fisher et al. (2021) with four receivers at the edges of a 250 m x 250 m square achieved an average accuracy of 50 m after applying correction factors. The error of ARTS varies depending on the setup density of the autonomous receiving stations and the signal strength of the transmitters. For regional scale ARTS, positioning errors typically span 1-15 km (Crewe et al., 2017). Whether the accuracy suffices for the study questions must be decided in each case. A pragmatic approach is to neglect the errors if their order of magnitude is much smaller than the animal movements studied (Fleming et al., 2020).  
The ARTS are less accurate than time-based GPS because they locate the transmitters based on bearing angles (Beardsworth et al., 2022). Slight imprecisions in bearing angles cause position errors, and these errors grow with the distance to the receivers (Beardsworth et al., 2022; Lenske and Nocera, 2018). Additional sources of errors are vegetation cover that alters the strength of radio signals and man-made signal noise (Kays et al., 2015). Every ARTS setup has a different accuracy because of hardware and local conditions, such as topography. Compared to GPS technology, ARTS are therefore not a ‘ready-to-use’ solution. They require extensive customization and quality control.  
One major problem is that users risk insufficient testing of ARTS. They are aware of accuracy variance between systems and over the course of a study (Heim et al., 2023). However, many wildlife telemetry studies do not report estimates of their local positioning errors; in the analysis, data are treated as error-free (Findholt et al., 2002; Bartolommei et al., 2012). These studies often apply signal noise filters during pre-processing of raw ARTS data to reduce positioning errors, but they do not further address how the positioning errors affect the positioning. There have long been efforts to standardize data and methods for a structured paradigm in movement ecology (Nathan et al., 2008; Udyawer et al., 2018). However, the proliferation of new ARTS has prevented the introduction of user-friendly protocols. There have been few attempts to systematize data processing and quality control. Gupte et al. (2022) developed a guideline for a high-throughput reverse GPS tracking system, which helps users pre-process the large amounts of data and calculate errors. The method, however, has limited applicability to other positioning systems, and no comparable work is available for ARTS, to date.  
My approach provides users with a result-oriented procedure for processing ARTS raw data. It allows error detection, error documentation and problem-solving. The user-friendly workflow helps to avoid losing track of the large amounts of data generated by high-throughput systems. They increase the reliability of ARTS, as unforeseen problems often occur with new automated systems. Therefore, the best practice is routinely integrating tests. Identifying sources of errors that occur in the field will help to report them to the ARTS developers. A link between users and developers will improve ARTS software and hardware in the future.  
In this thesis, I present a framework for filtering ARTS data for erroneous positioning data. I present how ARTS users can use exploratory data analysis to determine filter limits and settings. The filtering process uses ground truth data to quantify the accuracy of the positions calculated by ARTS and to estimate the antenna range. Given the relevance of such ground truth data, I describe in detail the sampling procedure for their acquisition. It includes the GPS positions of mobile and stationary test transmitters and the positions of birds detected by manual telemetry. Combining several complementary sampling methods of ground truth data allows a comprehensive view of the reliability of the ARTS and a differentiation among alternative sources of positioning error. The individual filtering steps provide users with pragmatic solutions to their study needs. The second part of the thesis covers a worked-out application example. I examine a newly constructed setup of the open-source ARTS after Gottwald et al. (2019). It operated in the summer and autumn of 2022 for the small-scale tracking of passerine birds in an intensive agricultural landscape. I process the data using my framework and evaluate the ARTS based on the example setup.  

# Methods

## stations
### quadrologgers
A station with 4 directional antennas, usually facing north, east, south, and west. Antennas used were **Yagi** antennas (decribe model and type, e.g. refer to already existing paper with same setup)   
*--> show picture of antenna beams (by Ralf)*


### monologgers
A station with 1 omnidirectional antenna facing upwards. Antennas used were **????** antennas (describe model and type, e.g. refer to already existing paper with same setup)  
*--> show picture of antenna beam (tRackIT??)*  

## tags
*--> describe different types of testtags (for maisC and D same models, melons has different ones)*

## sample sites
*--> maybe make a table to compare the different sites with columns no. of quadrologgers, no. of monologgers, no. and type of testtags, no. of testtracks, no. of circle tracks, no. of grid points (and distance between them), site description (e.g. difference in elevation, vegetation, ...)*  

```{r tabsite, echo=F}
kable(tab.site)
# kable(tab.site, 
#       # format = "latex", 
#       booktabs = T, linesep = "") %>%
#   add_header_above(c(" " = 5, "stations" = 2, " " = 1, "groundtruth data" = 3)) %>%
#   kable_styling(font_size = smallT,
#                 latex_options = c("striped", "repeat_header")) # repeat_header = repeats header when several pages
  
```

```{r figsite, echo=F}
# https://r-graph-gallery.com/182-add-circles-rectangles-on-leaflet-map.html
# https://rstudio.github.io/leaflet/articles/markers.html
m <- leaflet() %>% setView(lng = 14.45, lat = 52.53, zoom = 13)

leaflet(data = df.stat[df.stat$analysis == "yes",]) %>%
   addTiles() %>%
   addMarkers(~station.lon, ~station.lat , popup = ~as.character(station.id))

```


### maisC
- **10 quadrologgers** (maybe only 7 will be used due to twisted stations)  
- **10 monologgers** (maybe only 7 corresponding stations will be used)  


3-4 testtags at different heights (0.5m, 1m, 1.5m, 2m)  

- **XX testtracks**  
- **circle tracks** for stations c1l1-c6l1 (50m, 100m, 150m)  
- **gridpoints** with 100m distance to each other within a 300m (or 400m???) radius around all stations  

### maisD
- **8 quadrologgers**  


3 testtags at different heights (0.5m, 1m, 1.5m)  

- **XX testtracks**  
- **circle tracks** for all stations (50m, 100m, 150m)  
- **gridpoints** with 100m distance to each other within a 300m (or 400m???) radius around all stations  

### melons
- **xx quadrologgers** (ask Paula)  


xx testtags at different heights (???)  

- **XX testtracks**  
- **circle tracks** for xx stations (50m, 100m, 150m)  
- **gridpoints** with ???m distance to each other within a 300m (or 400m???) radius around all stations  

## preparation of data
*--> explain filtering process done by tRackIT*  

## position estimation
We used xx different approaches for positions estimations, namely  

- **bearings and triangulations**, e.g. method xx and method xy  
- **antenna beams** for quadrologgers   
- **multilateration** (e.g. another name) for monologgers  
- **mix of both**  
- ...   

*--> make a table as overview (e.g. which method is used for which type of station, ...)*  

## comparison of methods

### bearing accuracy

For bearing and triangulation methods only. Uses deviance between true angle (based on GPS position) and estimated angle. Should be accumulated around 0. If it is constantly shifted to the left or right, this might be an indicator that the antenna itself was shifted by some degrees. This might be used as a correction factor (also for other approaches) to redefine the northern orientation. If it shifts over time, one might either consider using different correction factors for the northern orientation over time or to exclude the station

### position accuracy

For all methods.



# Results



# Discussion



# References
